### 2024-02-19 documentation/thesis/thesis_document.tex
.

\begin{itemize}
\tightlist
\item
  \emph{Raspberry Pi OS Lite} - \gls{os} \emph{Debian bookworm x64}
\item
  \gls{mrp}-library described in chapter
  \ref{software-readout-framework} - Version \emph{1.4.1}
\item
  Unified Sensor-firmware described in chapter \ref{unified-sensor} -
  Version \emph{1.0.1}
\end{itemize}

@@

Once the hardware has been prepared, the task of the firmware of each of
the chained sensors is to find a common synchronisation clock. The
figure
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
illustrates how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The firmware-function
\emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the functionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

\begin{longtable}[]{@{}llll@{}}
\caption{Build hardware sensors equipped with different sensor \gls{ic}s
to cover various magnet charaterisation setups
\label{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}}\tabularnewline
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-full-sphere}\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-full-sphere}\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30mm & Cubic 30x30x30mm & Cubic
20x20x20mm\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following chapter shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter shown in figure
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
is used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}. This connectivity
makes it possible to make the device compatible with the unified sensor
ecosystem using a separate
\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{interface software}
executable on the host \gls{pc}. However, it does not offer the range of
functions that the unified sensor firmware offers.

@@

The following example shows the advantages of using the \emph{User
interaction points}:

A project called \emph{HalbachOptimisation} \customcite{O24} implements a
data analysis step and optimizes a magnetic field that is as homogeneous
as possible within a circular section using given mechanical dimensions
as input parameters of the magnets which are used. For this purpose, a
mutation of the magnet positions and rotations is performed. The result
is a list of positions for each magnet.

The \emph{MWO24} \customcite{MWO24} is an opensource project and generates
basic \gls{cad} drawings for \gls{mri} magnets in a Halbach
configuration. To do this, the number of magnets and additional
parameters for the properties of the \gls{cad} model to be created are
passed to the function provided as input parameters using a \gls{json}
file. The result is an \emph{OpenSCAD} \customcite{MMN19} based 3D model
of the magnet holder.

As a result, there are two projects which are both suitable for the task
of optimizing and creating Halbach magnets for \gls{mri} applications.
The data structures are not compatible with each other. However, they
are executed manually one after the other to obtain a result with manual
data conversation.

The library created is intended to solve this compatibility problem by
providing standardized and flexible data structures with this format of
magnetic field data. By separating the processing pipeline into defined
sub-steps, it is feasible to connect individual modules and as a result
functionalities interchangeable by the user.

The implementation of the same functionalities appears as the following
by using the library:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Create a static set of magnets}
\end{enumerate}

The input parameters of the \emph{HalbachOptimisation} \customcite{O24}
project are on the one hand the mechanical dimensions and the number of
magnets to be used. Idal magnets are assumed at this point. However, it
should also be possible to import field data in a more measured form
later. Using the data aquisition sub-step, it is possible to generate
any number of ideal magnets.

@@

Next, the user creates his own analysis step to be able to call up its
functions. In the case of the \emph{HalbachOptimisation} \customcite{O24}
project, the function signature of the start function must be changed.
This receives the result of the previous step, in this case the
generated magnet data. By optionally setting meta data in the universal
library data type, constants can be replaced in the analysis function
and made dynamically configurable. The return result also corresponds to
this data type so that subsequent steps are compatible and contains the
magnet data with modified position and rotation data.

@@

The last step is to call up the \emph{MWO24} \customcite{MWO24} project,
which creates the \gls{cad} model of the magnet holder. The data can
also be exported as files. To make the project compatible, the function
signatures are also adapted. In this case, more changes are required, as
the configuration file is loaded from the file system. This logic needs
to be removed to use the added meta data as input parameter instead.

@@

This also fulfils the goal of making individual user-created algorithms
interchangeable. If the user now wishes to use a different \gls{cad}
algorithm instead of the example \emph{HalbachMRIDesigner}
\customcite{MWO24} project, the other steps can simply be preserved and
only the new step needs to be implemented.

@@

In order to realise the concept of user interaction points, the library
is divided into different modules. These modules can be divided into two
main categories:

@@

Another important aspect for using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface.

If several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock as described in chapter
\ref{sensor-synchronisation-interface}. This no longer works for long
distances and the synchronisation must be established via a shared
network connection.

If time-critical synchronisation over the network is required, \gls{ptp}
and \gls{pps} output functionality \customcite{O24} can be used on many
\gls{sbc}, such as the \emph{Raspberry Pi Compute Module}.

@@

\hypertarget{construct-the-sensor-id-lookup-table}{%
\subsubsection{Construct the Sensor ID
Lookup-Table}\label{construct-the-sensor-id-lookup-table}}

Immediately after starting the \emph{MRPProxy}, the \gls{uuid}s of all
locally connected sensors are read out. These are stored together with
the class instance of the \emph{MRPHal} module in a \gls{lut}. This
makes it possible to address a sensor directly using its \gls{uuid}.

@@

@@

When using sensors with different capabilities, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \emph{info} command of each sensor is
queried. This information is added to the previously created \gls{lut}.
Duplicate entries are summarised (see table
\ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
host when the \emph{info} \ref{lst:mtsc} command is received over
network.

@@

These are converted into a Markdown format in an intermediate step and
this also allows to add further user documentation such as examples or
installation instructions.

Once the finished documentation has been generated from static
\gls{html} files, it is stored in the project repository. Another
publication option is to host the documentation via online services such
as \href{https://readthedocs.com}{ReadTheDocs}, where users can make
documentation for typical software projects available to others.

The documentation has also been uploaded to the
\href{https://magneticreadoutprocessing.readthedocs.io/}{ReadTheDocs}
service. The figure
\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
shows a screenshot of the start page, which also lists separate menu
items for tutorials on the individual functionalities.

The process of creating and publishing the documentation has been
automated using
\href{https://github.com/features/actions}{GithubActions}, so that it is
always automatically kept up to date with new features.

@@

This thesis describes the development of a universal Python library that
can be used to efficiently process data from magnetic field sensors from
acquisition to analysis. To ensure a practical application and allow
users to acquire their own magnetic field data directly, a low-cost and
easily reproducible hardware is also developed. The hardware is based on
widely used consumer magnetic field sensors and low-cost
microcontrollers, enabling an easily expandable and applicable solution
for measuring magnets with repeatable accuracy. Special attention is
paid to the expandability by the user. Interchangeable modules allow the
user to develop their own analysis algorithms without having to design
everything from scratch. The software framework was evaluated on the
basis of the previously defined use cases. A user-defined sorting
algorithm was implemented and integrated into the framework. The result
is a list of the magnets that deviate least from the magnetic strength.
The result was successfully verified by means of manual checks for
various other series of measurements. In this way, extensibility and
customisability were also successfully demonstrated during the software
evaluation. This underlines the power of the developed framework and
shows that it is not only effective in processing magnetic field sensor
data, but also provides a flexible platform for the implementation of
user-specific analyses. Subsequently, the developed framework was used
to automatically characterise various magnetic field sensors. For this
purpose, the developed pipeline feature of the software was used to
determine various sensor characteristics, including background noise,
temperature coefficients and linearity. The evaluation of the
measurement data showed that the selected sensors only partially fulfil
the defined requirements. Based on these results, it is proposed to
characterise further digital and analogue sensors, in particular
analogue magnetic field sensors with separate bias voltage. Alternative
methods for sensor adaptation are described in order to be able to use
these widely used consumer magnetic field sensors for the
characterisation of neodymium magnet-based permanent magnets.

>>>>

\begin{itemize}
\tightlist
\item
  \emph{Raspberry Pi OS Lite} - \gls{os}
\item
  \gls{mrp}-library described in chapter
  \ref{software-readout-framework} - Version \emph{1.4.1}
\item
  Unified Sensor-firmware described in chapter \ref{unified-sensor} -
  Version \emph{1.0.1}
\end{itemize}

@@

Once the hardware has been prepared, the task of the firmware of each of
the chained sensors is to find a common synchronisation clock. The
figure
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
illustrates how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The internal
firmware-function \emph{register irq on sync pin} is overwritten. To set
one \emph{primary} and several \emph{secondary} sensors, each sensor
waits for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the functionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

\begin{longtable}[]{@{}llll@{}}
\caption{Build hardware sensors equipped with different sensor \gls{ic}s
to cover various magnet charaterisation setups
\label{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}}\tabularnewline
\toprule
& 1D: single sensor & 1D: dual sensor & 3D: Fullsphere\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D: single sensor & 1D: dual sensor & 3D: Fullsphere\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30mm & Cubic 30x30x30mm & Cubic
20x20x20mm\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following chapter shows how existing hardware can be
integrated into the system. A temperature-compensated \emph{Voltcraft
GM-70} telsameter shown in figure
\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board_using_a_(+usb)_to_serial_converter_and_needed_additional_pull-up_resistors.png}
is used, which has a measuring range of \emph{0T} to \emph{3T} with a
resolution of \emph{0.1mT}. It offers an \emph{RS232} interface with a
documented protocol for connection to a \gls{pc}. This connectivity
makes it possible to make the device compatible with the previously
build unified sensor firmware using a separate
\href{https://github.com/RBEGamer/VoltcraftGM70Rest}{VoltcraftGM70Rest interface software}
executable on the host \gls{pc}. However, it does not offer the range of
functions that the unified sensor firmware offers.

@@

The following example shows the advantages of using \emph{user
interaction points}. In the following, two different projects are shown,
which are based on each other in terms of their functions for analysing
and optimising magnetic fields, but they are not compatible with each
other due to the different data formats and programming paradigms used.

The first project is a project called \emph{HalbachOptimisation}
\customcite{O24} implements a data analysis step and optimizes a magnetic
field that is as homogeneous as possible within a circular section using
given mechanical dimensions as input parameters of the magnets which are
used. For this purpose, a mutation of the magnet positions and rotations
is performed. The result is a list of positions for each magnet.

The \emph{HalbachMRIDesigner} \customcite{MWO24} is an opensource project
and generates basic \gls{cad} drawings for \gls{mri} magnets in a
Halbach configuration. To do this, the number of magnets and additional
parameters for the properties of the \gls{cad} model to be created are
passed to the function provided as input parameters using a \gls{json}
file. The result is an \emph{OpenSCAD} \customcite{MMN19} based 3D model
of the magnet holder.

As a result, there are two projects which are both in combination
suitable for the task of optimizing and generating Halbach magnets for
\gls{mri} applications. The data structures are not compatible with each
other and are usually executed manually one after the other by the user
in order to obtain a result, whereby additional manual data conversion
is required.

The \gls{mrp}-library solve this compatibility problem by providing
standardized and flexible data structures for of magnetic field data and
specified data flow guidelines.

The functionalities mapped by the two projects mentioned can be broken
down into the following steps so that an optimised Halbach array can be
generated from magnetic field data. The implementation of the same
functionalities from the mentioned projects above looks as follows when
using the \gls{mrp}-library:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Create magnetic field data}
\end{enumerate}

The input parameters of the \emph{HalbachOptimisation} \customcite{O24}
project are the mechanical dimensions and the number of magnets to be
used. Ideal magnets are assumed at this point. However, it should also
be possible to import measured magnetic field data from measured
magnets. Using the \gls{mri}-library data aquisition sub-step, it is
possible to generate any number of ideal magnets or import measured
magnets using sensor data from hardware sensors (see chapter
\ref{example-sensors}).

@@

Next, the user creates his own analysis step to be able to call up its
functions. In the case of the \emph{HalbachOptimisation} \customcite{O24}
project, the function signature of the start function must be changed.
This receives the result of the previous step, in this case the
generated magnet data. By optionally setting meta data in data type,
constants can be replaced in the analysis function and made dynamically
configurable. The return result also corresponds to the same data type
so that subsequent steps are compatible and contains the magnet data
with modified position and rotation data.

@@

The last step is to call the \emph{MWO24} \customcite{MWO24} project,
which creates the \gls{cad} model of the magnet holder and the model can
be exported as file. To make the project compatible, the function
signatures are adapted. In this case, more changes are required, as the
configuration file is loaded from the file system. This logic needs to
be removed to use the added meta data as input parameter instead.

@@

This also fulfils the goal of making individual user-created algorithms
interchangeable. If the user wishes to use a different \gls{cad}
algorithm instead of the example \emph{HalbachMRIDesigner}
\customcite{MWO24} project, the other steps can simply be preserved and
only the new step needs to be implemented.

@@

In order to realise the concept of \emph{user interaction points} from
chapter \ref{user-interaction-points}, the library is divided into
different modules. These modules can be divided into two main
categories:

@@

Another important aspect for using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface. If
several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock as described in chapter
\ref{sensor-synchronisation-interface}. This no longer works for long
distances and the synchronisation must be established via a shared
network connection. If time-critical synchronisation over the network is
required, \gls{ptp} and \gls{pps} output functionality \customcite{O24}
can be used on many \gls{sbc}, such as the \emph{Raspberry Pi Compute
Module}.

@@

@@

Immediately after starting the \emph{MRPProxy}, the \gls{uuid}s of all
locally connected sensors are read out. These are stored together with
the class instance of the \emph{MRPHal} module in a \gls{lut}. This
makes it possible to address and interact with a sensor directly using
its \gls{uuid}.

@@

When using sensors with the same capabilities, these must be combined.
These are used to select the appropriate measurement mode for a
measurement. For this purpose, the \emph{info} command of each sensor is
queried. This information is added to the previously created \gls{lut}.
Duplicate entries are summarised (see table
\ref{Sensor_capabilities_merging_algorithm.csv}) and returned to the
host when the \emph{info} \ref{lst:mtsc} command is received over
network.

@@

These are converted into a Markdown format in an intermediate step and
this also allows to add further user documentation such as examples or
installation instructions. Once the finished documentation has been
generated from static \gls{html} files, it is stored in the project
repository. Another publication option is to host the documentation via
online services such as \href{https://readthedocs.com}{ReadTheDocs},
where users can make documentation for typical software projects
available to others.

The documentation has also been uploaded to the
\href{https://magneticreadoutprocessing.readthedocs.io/}{ReadTheDocs}
service. The figure
\ref{MagneticReadoutProcessing_documentation_hosted_on_ReadTheDocs.png}
shows a screenshot of the start page, which also lists separate menu
items for tutorials on the individual functionalities. The process of
creating and publishing the documentation has been automated using
\href{https://github.com/features/actions}{GithubActions}, so that it is
always automatically kept up to date with new features.

@@

This thesis describes the development of a \gls{mrp} Python library that
can be used to efficiently process data from magnetic field sensors from
acquisition to analysis. To ensure a practical application and allow
users to acquire their own magnetic field data directly, a low-cost and
easily reproducible hardware is also developed. The hardware is based on
widely used consumer magnetic field sensors and low-cost
microcontrollers, enabling an easily expandable and applicable solution
for measuring magnets with repeatable accuracy. Special attention is
paid to the expandability by the user. Interchangeable modules allow the
user to develop their own analysis algorithms without having to design
everything from scratch. The software framework was evaluated on the
basis of the previously defined use cases. A user-defined sorting
algorithm was implemented and integrated into the framework. The result
is a list of the magnets that deviate least from the magnetic strength.

The result was successfully verified by means of manual checks for
various other series of measurements. In this way, extensibility and
customisability were also successfully demonstrated during the software
evaluation. This underlines the power of the developed framework and
shows that it is not only effective in processing magnetic field sensor
data, but also provides a flexible platform for the implementation of
user-specific analyses. Subsequently, the developed framework was used
to automatically characterise various magnetic field sensors. For this
purpose, the developed pipeline feature of the software was used to
determine various sensor characteristics, including background noise,
temperature coefficients and linearity.

The evaluation of the measurement data showed that the selected sensors
only partially fulfil the defined requirements.

The \emph{TLV493D} and \emph{MMC5603NJ} sensors are both suitable for
characterising permanent magnets and enable linearity compensation with
a defined measurement setup. Although the \emph{MMC5603NJ} has a limited
measuring range, it can still be used for relative comparisons of
permanent magnets without additional devices and without software
calibration. It also has a minimal long-term background noise. Absolute
comparability can be achieved by prior software calibration and using
reference measurements, making it an ideal sensor for the task of
characterising permanent magnets in field tests.

The \emph{MMC5603NJ} is not recommended for measuring the homogeneity of
a \emph{50\(\mu\)T} \emph{B0} field on a Halbach ring basis with an
accuracy of better than \emph{1000 \gls{ppm}} due to its limited
measuring range. The \emph{TLV493D} sensor, on the other hand, has too
much noise. It has been shown that this can be compensated for by
software calibration and long-term averaging of measured values. Despite
constant ambient conditions, temperature compensation is necessary for
this sensor. Due to the large measuring range and the constant
linearity, no software compensation is necessary. These results show
that the analysed sensors are generally suitable for the application
scenarios using the developed \gls{mrp} library with some limitations.

Based on these results, it is proposed to characterise further digital
and analogue sensors, in particular analogue magnetic field sensors with
separate bias voltage. Alternative methods for sensor adaptation are
described in order to be able to use these widely used consumer magnetic
field sensors for the characterisation of neodymium magnet-based
permanent magnets.
